---
title: "QP Data Analysis"
author: "Diana Sanchez"
date: "August 2022"
output: html_document
---


rm(list = ls(all.names = TRUE)) #clear R environment


# Load libraries
```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(GGally)
library(speakr)
library(dplyr)
library(tidyverse)
library(readr)
library(plyr)
library(stringi)
library(purrr)
library(broom)
library(scatterplot3d)

library(tidyr)
library(readr)
library(readxl)
```



#Analysis of all_data 
## Tidy all_data
all_data df includes all 58 participants, two groups. Only total correct responses are included for each experimental task (flanker, stroop, backward).
```{r}
#Load working data
all_data <- read.csv("/Users/princesa/Desktop/diana/all_data.csv", header = TRUE)

#summary
summary(all_data)

#separate groups: nonLanguage teachers and language teachers
nonLanguage <- all_data[1:36, ]
language <- all_data[37:58, ]

nonLanguage$language = "NonLanguage"
language$language = "Language"

#adding column to indicate nonLanguage or language for each participant
all_data = bind_rows(nonLanguage,language)
```

##Data Visualization of all participants with ggplot
```{r}
#all_data plot
ggplot(all_data, aes(x = age, y = IQ)) +
  #geom_jitter(width = .2)
  geom_point(size = 1) +
   ggtitle("Language Plot")
  #geom_smooth(method = "") +
  #facet_grid(language~backward_correct)
```

# Analsyis by groups
Data Analysis for nonLanguage Group {.tabset}
The nonLanguage group consist of the teachers who only use one language in their professional work setting.

## Linear regression model for nonLanguage BACKWARD task
```{r}
data(nonLanguage)
head(nonLanguage)

##plot
plot(backward_correct ~ age + IQ, data = nonLanguage, pch=16)

#linear model
backward_model_nonLanguage <- lm(backward_correct ~ age + IQ, data = nonLanguage)
#abline(backward_model_nonLanguage)

my_results <- tidy(backward_model_nonLanguage)
my_results
backward_model_nonLanguage

summary(backward_model_nonLanguage)

par(mfrow = c(2,2)) 
plot(backward_model_nonLanguage) 

AIC(backward_model_nonLanguage)
BIC(backward_model_nonLanguage)
```

## Linear regression model for nonLanguage FLANKER task
```{r}
data(nonLanguage)
head(nonLanguage)

##plot
plot(flanker_correct ~ age + IQ, data = nonLanguage, pch=16)

#linear model
flanker_model_nonLanguage <- lm(flanker_correct ~ age + IQ, data = nonLanguage)
#abline(flanker_model_nonLanguage)

my_results <- tidy(flanker_model_nonLanguage)
my_results
flanker_model_nonLanguage

summary(flanker_model_nonLanguage)

par(mfrow = c(2,2)) 
plot(flanker_model_nonLanguage) 

AIC(flanker_model_nonLanguage)
BIC(flanker_model_nonLanguage)

```

## Linear regression model for nonLanguage STROOP task
```{r}
data(nonLanguage)
head(nonLanguage)

##plot
plot(stroop_correct ~ age + IQ, data = nonLanguage, pch=16)

#linear model
stroop_model_nonLanguage <- lm(stroop_correct ~ age + IQ, data = nonLanguage)
abline(stroop_model_nonLanguage)

my_results <- tidy(stroop_model_nonLanguage)
my_results
stroop_model_nonLanguage

summary(stroop_model_nonLanguage)

par(mfrow = c(2,2)) 
plot(stroop_model_nonLanguage) 

AIC(stroop_model_nonLanguage)
BIC(stroop_model_nonLanguage)
```


# Data Analysis for Language Group {.tabset}
The language group consist of the teachers who use more than one language in their professional work setting.

## Linear regression model for language BACKWARD
```{r}
data(language)
head(language)

#plot Language
plot(backward_correct ~ age + IQ, data = language, pch=16)

#linear model
backward_model_language <- lm(backward_correct ~ age + IQ, data = language)
abline(backward_model_language)

my_results <- tidy(backward_model_language)
my_results
backward_model_language

summary(backward_model_language)

par(mfrow = c(2,2)) 
plot(backward_model_language) 

AIC(backward_model_language)
BIC(backward_model_language)
```

## Linear regression model for language FLANKER
```{r}
data(language)
head(language)

#plot Language
plot(flanker_correct ~ age + IQ, data = language, pch=16)

#linear model
flanker_model_language <- lm(flanker_correct ~ age + IQ, data = language)
abline(flanker_model_language)

my_results <- tidy(flanker_model_language)
my_results
flanker_model_language

summary(flanker_model_language)

par(mfrow = c(2,2)) 
plot(flanker_model_language) 

AIC(flanker_model_language)
BIC(flanker_model_language)
```

## Linear regression model for language STROOP
```{r}
data(language)
head(language)

#plot Language
par(mfrow = c(2,2))
plot(stroop_correct ~ age + IQ, data = language, pch=16)

#linear model
stroop_model_language <- lm(stroop_correct ~ age + IQ, data = language)

par(mfrow = c(2,2))
plot(stroop_model_language)

my_results <- tidy(stroop_model_language)
my_results
stroop_model_language

summary(stroop_model_language)

par(mfrow = c(2,2)) 
plot(stroop_model_language) 

AIC(stroop_model_language)
BIC(stroop_model_language)
```


#ADDITIONAL ANALYSIS

## Histogram to observe results
```{r}
attach(all_data) #using objects in df all_data
hist(backward_correct) #this could be considered "normal"
hist(flanker_correct) #not normal
hist(stroop_correct) #not normal

summary(all_data)
```


# normalize data
Attempted to normalize data to see if it would make a difference.
```{r}
attach(all_data)
scaledflank <- scale(flanker_correct)
scaledstroop <- scale(stroop_correct)
scaledback <- scale(backward_correct)

lang = substring(participant,1,3)=="bi_"
biling = rep("false",length(lang)) #make this variable all FALSE

biling[lang]="true" #
data <- data.frame(age,IQ,scaledflank,scaledstroop,scaledback,biling)
#colnames(data)=c("age","IQ","scaledflank","scaledstroop","scaledback","biling") #not needed but may use later

hist(scaledback)
hist(scaledstroop)
hist(scaledflank)

```




#------------------------------------------##
TESTING Additional plots
```{r}
ggplot(data = all_data) +
  geom_point(mapping = aes(x = backward_correct, y = IQ, color = age))


scatterplot3d(
  all_data[1:4], pch = 19, color = "steelblue",
  grid = TRUE, box = FALSE,
  mar = c(3, 3, 0.5, 3)
)


# nonLanguage Scatterplot
ggplot(nonLanguage, aes(backward_correct, IQ)) +
  geom_point(fill = "dark green", color = "black",
             size = 5, shape = 21) +
  ggtitle("LanguagePlot")

```




#------------------------------------------------------------------------#

# Removing 1 data (45) which may be an outlier. This was done just to observe if it would result in a difference in results.

##Removing line 45
```{r}
#created new data with deleted row 45
new_all_data <- all_data[-c(45),]

#created new language group (-45)
new_language <- new_all_data[37:58, ]


#plot Language
plot(flanker_correct ~ age + IQ, data = new_language, pch=16)

#linear model
flanker_model_language <- lm(flanker_correct ~ age + IQ, data = new_language)
abline(flanker_model_language)

my_results <- tidy(flanker_model_language)
my_results
flanker_model_language

summary(flanker_model_language)

par(mfrow = c(2,2)) 
plot(flanker_model_language) 


##
#plot Language
par(mfrow = c(2,2))
plot(stroop_correct ~ age + IQ, data = new_language, pch=16)

#linear model
stroop_model_language <- lm(stroop_correct ~ age + IQ, data = new_language)

par(mfrow = c(2,2))
plot(stroop_model_language)

my_results <- tidy(stroop_model_language)
my_results
stroop_model_language

summary(stroop_model_language)
```










